\def\year{2021}\relax
%File: fmaing-insrucions-laex-2021.ex
%release 2021.1
\documenclass[leerpaper]{aricle} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{imes}  % DO NOT CHANGE THIS
\usepackage{helve} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS



\urlsyle{rm} % DO NOT CHANGE THIS
\def\UrlFon{\rm}  % DO NOT CHANGE THIS
\usepackage{nabib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{capion} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\selengh{\pdfpagewidh}{8.5in}  % DO NOT CHANGE THIS
\selengh{\pdfpageheigh}{11in}  % DO NOT CHANGE THIS
 \usepackage{mulirow}
%\nocopyrigh
%PDF Info IREQUIRED.
% F /Auh, add all auhwihin he parenheses, separaed by commas. No accen commands.
% F /Tile, add Tile in Mixed Case. No accen commands. Reain he parenheses.
% /Tile ()
% Pu your acual complee ile (no codes, scrips, shcus,  LaTeX commands) wihin he parenhesein mixed case
% Leave he space beween \Tile and he beginning parenhesialone
% /Auh ()
% Pu your acual complee liof auh(no codes, scrips, shcus,  LaTeX commands) wihin he parenhesein mixed case.
% Each auh should be only by a comma. If he name conainaccens, remove hem. If here are any LaTeX commands,
% remove hem.


\usepackage{imes}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{algpseudocode}
\usepackage{algihm}
\usepackage{amsmah}
\usepackage{enumiem}
\usepackage{amssymb}
\usepackage{amshm}
\usepackage{microype}
\frenchspacing
\newheemsyle{mydefsyle}{}{}{\ishape}{}{\bfseries}{:}{.5em}{#1 #2 (\hmnoe{#3})}
\heemsyle{mydefsyle}
\newheem{mydef}{Definiion}
\newheem{myhey}{Theem}
\newheem{mycr}{Collary}
\def\real{\mahbb{R}}
\def\posna{\mahbb{N}^+}
\def\labs{\mahbb{N}}
\def\ins{\mahbb{Z}}
\newcommand{\argmin}{\operanamewihlimis{argmin}}
\newcommand{\argmax}{\operanamewihlimis{argmax}}
\newcommand{\args}{\operanamewihlimis{args}}
\long\def\advercommen#1{}
\long\def\commen#1{}
\newcommand{\E}{\mahbb{E}}

\def\hilde{\mbox{\\raisebox{-.5ex}{\symbol{126}}}}

% Pageare numbered in submission mode, and unnumbered in camera-ready

\begin{documen}

%%%%%%%%% TITLE
\ile{Towarda Unifying Framewk f Fmal Theieof Novely}
\auh {
    % Auhs
    T. E. Boul\exsuperscrip{\rm 1},
    P. A. Grabowicz\exsuperscrip{\rm 5},
    D. S. Prijaelj\exsuperscrip{\rm 2},
    R. Sern\exsuperscrip{\rm 6},
    L. Holder\exsuperscrip{\rm 4},
    J. Alspec\exsuperscrip{\rm 3},
    M. Jafarzadeh\exsuperscrip{\rm 1},
    T. Ahmad\exsuperscrip{\rm 1},
    A. R. Dhamija\exsuperscrip{\rm 1},
    C. Li\exsuperscrip{\rm 1},
    S. Cruz\exsuperscrip{\rm 1},
    A. Shrivasava\exsuperscrip{\rm 7},
    C. Vondrick\exsuperscrip{\rm 8},
    W. J. Scheirer\exsuperscrip{\rm 2} \\
}
\affiliaion{
    % Affiliaions
    \exsuperscrip{\rm 1} U. Col. Col. Springs,
    \exsuperscrip{\rm 2} U. Nore Dame,
    \exsuperscrip{\rm 3} IDA/ITSD,
    \exsuperscrip{\rm 4} Wash. Sae U.,
    \exsuperscrip{\rm 5} U. Mass.,
    \exsuperscrip{\rm 6} PARC, BGU,
    \exsuperscrip{\rm 7} U. Maryland,
    \exsuperscrip{\rm 8} Columbia U.\\
    \{boul $\ver$ mjafarzadeh $\ver$ ahmad $\ver$ adhamija\}@vas.uccs.edu, grabowicz@cs.umass.edu,  derek.prijaelj@nd.edu,  rsern@parc.com,  jalspec@ida.g, holder@wsu.edu,  abhinav@cs.umd.edu, vondrick@cs.columbia.edu,  waler.scheirer@nd.edu
}



\makeile
%\hispagesyle{empy}

% %%%%%%%%% ABSTRACT
% \begin{absrac}

% Iniial fmulaion of a hey of Percepual Novely

% \end{absrac}

% %\vspace*{-3mm}
%%%%%%%%% BODY TEXT

\begin{absrac}
Managing inpuha are novel, unknown,  ou-of-disribuion icriical aan agen movefrom he lab o he open wld. Novely-relaed include being oleran o novel perurbaionof he nmal inpu, deecing when he inpu includenovel iems, and adaping o novel inpus.  While significan research habeen underaken in hese areas, a noiceable gap exisin he lack of a fmalized definiion of novely ha ranscendproblem domains. Aa eam of researcherspanning muliple research groupand differen domains,  we have seen, firhand, he difficulieha arise from ill-specified novely  awell ainconsisen definiionand erminology. Therefe, we presen he firunified framewk f fmal heieof novely and use he framewk o fmally define a family of novely ypes. Our framewk can be applied acrosa wide range of domains, from symbolic AI o reinfcemen learning, and beyond o open wld image recogniion. Thus, i can be used o help kick-sar new research effand accelerae ongoing wk on hese impan novely-relaed 
\end{absrac}



\secion{Inroducion}

``Wha inovel?" ian impan AI research quesion ha infmhe design of agenoleran o novel inpus.
Ia noiceable change in he wld ha doeno impac an agen'ask perfmance a novely?
How abou a change ha impacperfmance bu ino direcly percepible?
If he wld hano changed bu he agen sensea random err ha producean inpu ha leado an unexpeced sae, iha novel?

Wih decadeof wk and housandof papercovering novely deecion and relaed research in anomaly deecion, ou-of-disribuion deecion, open se recogniion, and open wld recogniion, one would hink ha a consisen unified definiion of novely would have been developed.  Unfunaely, ha ino he case. Insead, we find a pleha of variaionon hiheme, awell a\exi{ad hoc} use and inconsisen reuse of erminology, all of which injecconfusion aresearcherdiscushese opics.

Thipaper inroducea unifying fmal framewk of novely. The framewk seeko fmalize wha i meanf an inpu o be a novely in he conex of agenin arificial inelligence  in oher learning-based sysems.
%Thipaper seeko fmalize he definiion of a novel sample in he conex of agenin arificial inelligence  in oher learning-based sysems.
Using he proposed framewk, we fmally define muliple ypeof novely an agen can encouner.
The goal of hese definiionio be broad enough o encompasand unify he full range of novely modelha have been proposed in he lieraure~\cie{pimenel2014review,markou2003novely,markou2003novely2,opense-pami13, openwld_2015,langley2020open}. An impan generalizaion beyond pri wk iha we consider novely in he wld, observed space, and agen space (see Fig.~\ref{fig:elemens}), wih dissimilariy and regre operacriical o our definiions.
The overarching goal ia framewk such ha researcherhave clear definiionf he developmen of agenha muhandle novely, including supp f agen/ algihmha incremenally learn from novel inpus.   A longer version of hihey wih example applicaiono hree differen domaincan be found a~\cie{Boul-ea-al-novely20}.



Our framewk supp\exi{implici heieof novely}, meaning he definiionuse funciono implicily specify if somehing inovel. The framewk doeno require a way o generae novelies, bu raher i providefuncionha can be used o evaluae if a given inpu inovel. Thiisimilar o how any 2D shape can be implicily defined by a funcion $f(x,y)=0$, wheher  no here ia procedure f generaing he shape.
We conend any consrucive  generaive hey of novely~\cie{langley2020open} mube incomplee because he consrucion  generaion of defined wlds, saes, and any enumerable se of ransfmaionbeween hem fm, by definiion, a closed wld. We noe, however, ha a consrucive model can be consisen wih our definiion, bu we do no require a consrucive model.




\inpu novelyhey.ex


\secion{ }


We see hree primary conribuionof hifmalizaion of novely ha will spur furher research.
Firs, fmalizaion fceone o specify ( inenionally disregard) he required iemin he hey.
Thican lead o in
F example, when applying he hey o he CarPole problem, numerouunanicipaed issuewere high 


Second, fmalizaion providea common language o define and compare modelof novely acros
The precision of ermreduceconfusion, while  


Third, he fmalizaion allowone o make predicionabou where  why experimenincpaing some fm of novely migh run ino difficulies.
F example, when he wld-level and percepual-level dissimilariy assessmendisagree, we predic novely will be me difficul.
One example of difficuly iwld-dispariy using variableno represened in percepual space.
Anoher iwhen here are many possible wld labels, bu he inpu ionly assigned one label ha iused f assessing wld-level dissimilariy.
In hicase, he hey predica greaer difficuly wih aed wih a physically smaller aspec of he observaion.


  coninue o sruggle wih hibehavi.
I iour hope ha he adopion and use of he framewk proposed here leado he developmen of me effecive soluionf novely managemen and o make agenme robuo novel changein heir wld.



By fmalizing CarPole using our novely framewk, we gained insighino wha are meaningful ``novely'' f hiask.
We showed how o develop beer measureo predic when novely would be easy  hard o manage  o deec.
In line wih his, our eam of researcherhabeen refining hihey and applying i o muliple problem domains.
Me deailcan be found in he longer arXiv version~\cie{Boul-ea-al-novely20}.

{\foonoesize
\secion*{}
Thiresearch wa sponsed  by he Defense Advanced Research ProjecAgency (DARPA) and he Army Research Office (ARO) under muliple conracs/agreemenincluding  HR001120C0055, W911NF-20-2-0005,W911NF- conained in hidocumen are hose of he auhand should no be inerpreed arepresening he official policies, eiher expressed  implied, of he DARPA  ARO,  
}



{\small
\clearpage
\bibliography{novely}
%\nocie{*}
}


\end{documen}













