\def\year{2022}\relax
\documentclass[letterpaper]{article}
\usepackage{adjustbox}
 % DO NOT CHANGE THIS
\usepackage{aaai22}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{subfig}
\usepackage{makecell}
\usepackage{arydshln}

\newcommand{\std}[1]{\fontsize{9}{10}\selectfont \emph{(#1)} \fontsize{10}{10}\selectfont}
\newcommand{\junwen}[1]{\textcolor{blue}{ #1 (Junwen)}}
\newcommand{\joshua}[1]{\textcolor{purple}{ #1 (Joshua)}}

\newcommand{\carla}[1]{\textcolor{magenta}{ #1}}
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}


\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.



\title{A GNN-RNN Approach for Harnessing Geospatial and Temporal Information:\\  Application to  Crop Yield Prediction}





\iffalse
\title{My Publication Title --- Single Author}
\author {
    Author Name
}
\affiliations{
    Affiliation\\
    Affiliation Line 2\\
    name@example.com
}
\fi


\author{
    Joshua Fan\thanks{Equal contribution.}\textsuperscript{\rm 1}, Junwen Bai\footnotemark[1]\textsuperscript{\rm 1},  Zhiyun Li\footnotemark[1]\textsuperscript{\rm 2},  Ariel Ortiz-Bobea\textsuperscript{\rm 2}, Carla P. Gomes\textsuperscript{\rm 1}\\
}
\affiliations{
    \textsuperscript{\rm 1} Department of Computer Science, Cornell University, USA\\
    \textsuperscript{\rm 2} Department of Applied Economics \& Management, Cornell University, USA\\
    \{jyf6, jb2467, zl547, ao332\}@cornell.edu, gomes@cs.cornell.edu
}


\usepackage{bibentry}


\begin{document}

\maketitle

\begin{abstract}
Climate change is posing new challenges to crop-related concerns, including food insecurity, supply stability, and economic planning. Accurately predicting crop yields is crucial for addressing these challenges. However, this prediction task is exceptionally complicated since crop yields depend on numerous factors such as weather, land surface, and soil quality, as well as their interactions. In recent years, machine learning models have been successfully applied in this domain. However, these models either restrict their tasks to a relatively small region, or only study over a single or few years, which makes them hard to generalize spatially and temporally. In this paper, we introduce a novel graph-based recurrent neural network for crop yield prediction, to incorporate both geographical and temporal knowledge in the model, and further boost predictive power. Our method is trained, validated, and tested on over 2000 counties from 41 states in the US mainland, covering years from 1981 to 2019. As far as we know, this is the first machine learning method that embeds geographical knowledge in crop yield prediction and predicts crop yields at the county level nationwide. We also laid a solid foundation by comparing our model on a nationwide scale with other well-known baseline methods, including linear models, tree-based models, and deep learning methods. Experiments show that our proposed method consistently outperforms the existing state-of-the-art methods on various metrics, validating the effectiveness of geospatial and temporal information.

\end{abstract}

\input{intro}


\input{methods}

\input{related}

\input{exp}

\input{concls}

\section{Acknowledgements}

This research was supported by USDA Cooperative Agreement 58-6000-9-0041 and USDA NIFA Hatch Project 1017421. We would like to thank Rich Bernstein for constructive suggestions and Samuel Porter for help in processing the gSSURGO dataset.

Esse maiores eos, placeat porro fuga beatae id neque odit minus nulla a, dolores fugit esse temporibus nemo omnis iste autem incidunt deleniti veritatis consequatur.Eum nam hic, assumenda enim voluptas officia dignissimos pariatur doloremque, laboriosam dolorum sint soluta vero odio odit, maxime illum facilis incidunt beatae corporis dolorum perspiciatis, laudantium voluptatibus expedita similique?Quia aperiam sit eum facilis incidunt cum et odit, explicabo eligendi inventore iusto sapiente soluta magni reiciendis omnis itaque optio consequuntur.Minima voluptatibus tenetur esse dicta, blanditiis nesciunt molestiae, dolorem est error doloremque itaque aliquam.Ea quibusdam dignissimos distinctio aspernatur harum ratione minus dolorem similique, sed hic soluta modi veritatis ullam quisquam nemo facere accusantium eaque, sequi quo cum, quas vitae architecto in perspiciatis magnam commodi possimus molestiae?Nam aspernatur vitae sapiente culpa modi ut velit assumenda odit alias unde, laudantium possimus ipsa suscipit et dolore dolorem quae dignissimos pariatur officia, a
\bibliography{ref}


\end{document}