\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
%\usepackage{parskip}
\usepackage{algorithm}
\usepackage{booktabs}
\usepackage{algorithmic}
\usepackage{comment}
\usepackage{wrapfig}
\usepackage[round]{natbib}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usepackage{fancyhdr}
\usetikzlibrary{shapes,arrows}
\pgfplotsset{compat=1.14}

\tikzstyle{block} = [rectangle, draw, 
    text width=6em, text centered, minimum height=3em]
\tikzstyle{dashblock} = [rectangle, draw, 
    text width=6em, text centered,dashed, minimum height=3em,node distance=1.1cm]
\tikzstyle{line} = [draw, -latex]
\tikzstyle{cloud} = [draw, ellipse, node distance=2cm,
    minimum height=2em]

\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Auditing News Curation Systems: A Case Study Examining Algorithmic and Editorial Logic in Apple News)
%/Author (anonymous)
/Author (Jack Bandy, Nicholas Diakopoulos)
}


\setcounter{secnumdepth}{0}  
\nocopyright

 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Apple News as Gatekeeper: An Audit Study}
%\title{Auditing Algorithmic News Curators: A Case Study of Apple News}
%\title{What's Trending in Apple News? Auditing Sociotechnical News Curation Systems}
\title{Auditing News Curation Systems:\\ A Case Study Examining Algorithmic and Editorial Logic in Apple News}

\author{Jack Bandy\\
{Northwestern University}\\
jackbandy@u.northwestern.edu,
\And
Nicholas Diakopoulos\\
{Northwestern University}\\
nad@northwestern.edu}

\fancypagestyle{plain}{
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} 
\chead{\small{\textit{To Appear in} Proceedings of the Fourteenth International AAAI Conference on Web and Social Media (ICWSM 2020)}}}

\maketitle\thispagestyle{plain}
\begin{abstract}
This work presents an audit study of Apple News as a sociotechnical news curation system that exercises gatekeeping power in the media. We examine the mechanisms behind Apple News as well as the content presented in the app, outlining the social, political, and economic implications of both aspects. We focus on the Trending Stories section, which is algorithmically curated, and the Top Stories section, which is human-curated. Results from a crowdsourced audit showed minimal content personalization in the Trending Stories section, and a sock-puppet audit showed no location-based content adaptation. Finally, we perform an extended two-month data collection to compare the human-curated Top Stories section with the algorithmically-curated Trending Stories section. Within these two sections, human curation outperformed algorithmic curation in several measures of source diversity, concentration, and evenness. Furthermore, algorithmic curation featured more ``soft news'' about celebrities and entertainment, while editorial curation featured more news about policy and international events. To our knowledge, this study provides the first data-backed characterization of Apple News in the United States. 
\end{abstract}


\input{intro.tex}

\input{related.tex}

\input{apple-news.tex}

\input{audit-framework.tex}

\input{audit-methods.tex}

\input{results.tex}

\input{discussion.tex}

\input{conclusion.tex}

\input{acknowledgements.tex}

\small{
\bibliography{library}
\bibliographystyle{aaai}
}
\end{document}