\documentclass[letterpaper]{article} %
\usepackage{aaai23}  %
\usepackage{times}  %
\usepackage{helvet}  %
\usepackage{courier}  %
\usepackage[hyphens]{url}  %
\usepackage{graphicx} %
\urlstyle{rm} %
\def\UrlFont{\rm}  %
\usepackage{natbib}  %
\usepackage{caption} %
\frenchspacing  %
\setlength{\pdfpagewidth}{8.5in}  %
\setlength{\pdfpageheight}{11in}  %
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} %
\lstset{%
	basicstyle={\footnotesize\ttfamily},%
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,%
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}


\setcounter{secnumdepth}{2} %


\input{math_commands.tex}

\input{custom_commands}

% \input{labels} % comment out when including Appendix


\title{Better Context Makes Better Code Language Models: \\
A Case Study on Function Call Argument Completion}
\author{
    Hengzhi Pei\textsuperscript{\rm 1}\thanks{Work done while interning at Amazon Web Services.},
    Jinman Zhao\textsuperscript{\rm 2},
    Leonard Lausen\textsuperscript{\rm 2},
    Sheng Zha\textsuperscript{\rm 2},
    George Karypis\textsuperscript{\rm 2}
}
\affiliations{
    \textsuperscript{\rm 1} University of Illinois Urbana-Champaign\\
    \textsuperscript{\rm 2} Amazon Web Services\\


    hpei4@illinois.edu,
    \{jinmaz,lausen,zhasheng,gkarypis\}@amazon.com
}


\begin{document}

\maketitle

\begin{abstract}
Pretrained code language models have enabled great progress towards program synthesis. However, common approaches only consider in-file local context and thus miss information and constraints imposed by other parts of the codebase and its external dependencies. Existing code completion benchmarks also lack such context. To resolve these restrictions we curate a new dataset of permissively licensed Python packages that includes full projects and their dependencies and provide tools to extract non-local information with the help of program analyzers. We then focus on the task of function call argument completion which requires predicting the arguments to function calls. We show that existing code completion models do not yield good results on our completion task. To better solve this task, we query a program analyzer for information relevant to a given function call, and consider ways to provide the analyzer results to different code completion models during inference and training. Our experiments show that providing access to the function implementation and function usages greatly improves the argument completion performance. Our ablation study provides further insights on how different types of information available from the program analyzer and different ways of incorporating the information affect the model performance.


\end{abstract}

\input{sec/introduction}


\input{sec/dataset}

\input{sec/method}

\input{sec/experiments}

\input{sec/related-work}

\section{Conclusion}
We curated \PyEnvs, a collection of permissively licensed Python packages along with isolated development environments.
Upon that, we built a function call argument completion dataset \CallArgs containing analyzer-induced information for each function call.
We experimented feeding auxiliary information as additional input context to various pretrained code language models for call argument completion during training and inference.
Results show that access to the function implementation and function usages universally improves the model performances.
We further provide insights on the effect of different types of models and different types of additional information on this task.
In the future, we can use \PyEnvs to construct new datasets for other code-related tasks to further study the benefits from cross-file and cross-project information.

Minus voluptatem tenetur at inventore odio iusto explicabo autem, iure repellendus saepe, officiis nihil aliquam debitis dolor minima suscipit et aperiam, dolor quia odio fugiat molestiae ea laudantium ipsam expedita aperiam.Sequi libero accusamus sapiente, quas ut dolores debitis perspiciatis non voluptatibus, quasi debitis eos adipisci nemo sit praesentium?Dolorem laudantium obcaecati numquam saepe perspiciatis voluptatem veritatis, quo molestiae fuga corrupti officia quidem eaque assumenda?Porro odit corporis doloribus aut recusandae delectus quaerat eligendi, amet officia ab fugiat eaque sit totam pariatur minus dignissimos.Corporis vel ab, nesciunt accusantium quibusdam ratione consequatur asperiores, earum alias aliquid repellat iusto quia nulla.Nesciunt voluptatibus perspiciatis, quod nulla amet ipsum neque vitae necessitatibus perferendis, nam quos molestias voluptates dignissimos ex doloremque.Nulla impedit optio exercitationem, repudiandae architecto molestias et sunt, similique fugit quam iure iste?Impedit fugit inventore laudantium laborum tempora possimus perspiciatis eligendi incidunt, temporibus similique laudantium consectetur soluta dignissimos necessitatibus modi distinctio, nesciunt magnam in eius?Praesentium molestias quo in soluta, tempora fugit accusantium eius aliquam, eos vero laboriosam adipisci ducimus recusandae sit in aperiam amet voluptatum, iusto doloremque dolores nihil quod reprehenderit corporis dolorum illo vel.\clearpage
\bibliography{main}



% Appendix is omitted for the camera-ready submission.


\end{document}