%File: formatting-instructions-latex-2024.tex
%release 2024.0
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai24}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}



\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
%\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[T1]{fontenc}
%\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithmic}
\usepackage{subfigure}



%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%
% Keep the \pdfinfo as shown here. There's no need
% for you to add the /Title and /Author tags.

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
%  -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
%  -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai24.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash

\title{Bias-Conflict Sample Synthesis and Adversarial Removal Debias Strategy for Temporal Sentence Grounding in Video}
%\title{\fontsize{14}{16}{\centering{Bias-Conflict Sample Synthesis and Adversarial Removal Debias Strategy for Temporal Sentence Grounding in Video}}}


\author{
	Zhaobo Qi\textsuperscript{\rm 1},
	Yibo Yuan\textsuperscript{\rm 1},
	Xiaowen Ruan\textsuperscript{\rm 1},
	Shuhui Wang\textsuperscript{\rm 2}, \\
	Weigang Zhang\textsuperscript{\rm 1}\thanks{Corresponding author.},
	Qingming Huang\textsuperscript{\rm 2, \rm 3 *}
}
\affiliations {
	\textsuperscript{\rm 1}Harbin Institute of Technology, Weihai, China\\
	\textsuperscript{\rm 2}Key Lab of Intell. Info. Process., Inst. of Comput. Tech., CAS, Beijing, China\\
	\textsuperscript{\rm 3}University of Chinese Academy of Sciences, Beijing, China\\
	%\textsuperscript{\rm 4}Peng Cheng Laboratory, Shenzhen, China\\
	qizb@hit.edu.cn, \{yuanyibo21,22s130489\}@stu.hit.edu.cn, wangshuhui@ict.ac.cn, \\ wgzhang@hit.edu.cn, qmhuang@ucas.ac.cn
}


% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry

\begin{document}

\maketitle

\begin{abstract}
	Temporal Sentence Grounding in Video (TSGV) is troubled by dataset bias issue, which is caused by the uneven temporal distribution of the target moments for samples with similar semantic components in input videos or query texts. Existing methods resort to utilizing prior knowledge about bias to artificially break this uneven distribution, which only removes a limited amount of significant language biases. In this work, we propose the bias-conflict sample synthesis and adversarial removal debias strategy (BSSARD), which dynamically generates bias-conflict samples by explicitly leveraging potentially spurious correlations between single-modality features and the temporal position of the target moments. Through adversarial training, its bias generators continuously introduce biases and generate bias-conflict samples to deceive its grounding model. Meanwhile, the grounding model continuously eliminates the introduced biases, which requires it to model multi-modality alignment information. BSSARD will cover most kinds of coupling relationships and disrupt language and visual biases simultaneously. Extensive experiments on Charades-CD and ActivityNet-CD demonstrate the promising debiasing capability of BSSARD. Source codes are available at~\url{https://github.com/qzhb/BSSARD}.
\end{abstract}



\input{Introduction}

\input{RelatedWork}

\input{Method}

\input{Experiment}



\section{Conclusion}
In this paper, we propose a novel adversarial training debias framework for TSGV task.
It dynamically generates bias-conflict samples by exploiting all kinds of spurious relationships between single-modality features and the target moments, which can effectively remove the bias dependency of the TSGV models.
In essence, the debias is achieved through directional data augmentation, which breaks the uneven temporal distribution of the target moments for samples that contain similar semantic components.
Extensive experiments on Charades-CD and ActivityNet-CD datasets demonstrate the effectiveness of our strategy.
In the future, we will apply our method to a wider range of scenarios, such as debias in visual question-answering task, and also eliminate cross-modality combination bias problems.



\section{Acknowledgments}
This work was supported in part by the National Natural Science Foundation of China under Grant U21B2038, 62306092, 61976069, 62022083, and 62236008.%, in part by the Research Start-Up Fund from Harbin Institute of Technology, Weihai under Grant IDGA10002144.



Vero modi repellendus eligendi, quaerat adipisci nobis accusamus maxime ex voluptatem laboriosam iure et nam, repellendus voluptatem quaerat reiciendis culpa distinctio optio, nisi illum dolor facilis nostrum accusamus, temporibus suscipit reprehenderit velit voluptatem.Perferendis animi reiciendis ea beatae possimus quia cupiditate quam quibusdam eveniet, inventore eum est quam, assumenda eaque officiis illo?Quod voluptates repellendus eius reiciendis aspernatur tempora assumenda, itaque dignissimos exercitationem?Eum nostrum eius aliquam doloremque veritatis laboriosam quisquam ipsum itaque, similique veritatis sed magni, quaerat mollitia ullam
\bibliography{aaai24}

\end{document}