\section{Motivating Study} 

% \subsection{Potential Urgent Situations \label{sec:motivation}} 
% Making seemingly routine calls to the local call center can conceal potentially urgent situations in various instances. Analysis of a large collection of audio transcriptions, conducted collaboratively with the call center team, reveals approximately 2,746 out of 4,640 transcriptions indicate possible urgent circumstances during the call. This finding highlights the urgency of developing an intelligible, manageable handover control system to promptly notify dispatchers when current calls imply urgent scenarios.


\subsubsection{Unintentional Additional Information}

 Examination of audio transcriptions indicates callers tend to provide supplementary details beyond the dispatcher's specific inquiries (72\% of callers offer extra information, exceeding the question's scope). Notably, this additional information can enhance the precision and comprehensiveness of the emergency response system. See the example below with the caller's personal information removed: 

$\mathsf{Dispatcher}$: Metro Nashville Police, Fire, and Medical, what is the location of your emergency? $\mathsf{Caller}$: Oh, I'm not sure if this is an emergency. I am \textit{\#name}, \textit{\#phone\_number}. The address is \textit{\#address}. It's the King Buffet. I got about a customer out in the parking lot smoking crackpipes in front of all the customers. 


% Here, despite the dispatcher asking about location, the caller additionallshares name, phone number, and suspicious activity details, hinting at a drug-related incident. Utilizing this information strategically could enhance emergency response talks, addressing follow-up queries preemptively, and streamlining interactions.

In this conversation turn, although the dispatcher only inquires about location, the caller provides additional details like name, phone number, and suspicious activity, suggesting a drug-related case. Strategically leveraging such extra information could optimize emergency response conversations by proactively addressing potential follow-up questions, thus streamlining the interaction. 

% Notably, only high-confidence answers undergo integration into the final report, achieved through an interactive confidence-checking process. This ensures maintained accuracy and reliability while restricting the final report to only the most relevant information.

\subsubsection{Shifting and Multiple Incident Types}
Call recordings show that ongoing incidents mentioned by callers occasionally encompass multiple incident types (at a rate of 38.27\%). Callers also tend to modify incident types as they uncover more details. For instance, phrases like ``someone busted my car and my wallet is gone'' indicate two incident types – damaged and lost stolen property. Similarly, in ``I saw a car illegally parked... oh, wait, it's abandoned because the bumper is off and rusted,'' the caller initially reports illegal parking, then recognizes it as an abandoned vehicle based on new details. This underscores the need for our system to recognize various incident types concurrently and adapt to evolving conversations.


% Based on the call recordings, the ongoing incident happening on the caller's side sometimes refers to multiple incident types (with a percentage of 38.27\%). Meanwhile, the caller might also tend to change the incident type with more details discovered. For example, ``...someone busted my car and my wallet is gone...'' indicates two incident types – ``someone busted my car'' suggests damage to property while ``my wallet is gone'' implies lost or stolen property. Also, in ``... I saw a car illegally parked at the same spot in the garage for a while... oh, wait I think it is abandoned instead cuz the bumper is off and rusted ...'', the caller was to report an illegal parking case, but then figured out this should be reported as an abandoned vehicle based on details like ``the bumper is off and rusted.'' This discovery necessitates that our system possesses the capability to simultaneously identify various types of incidents while also being adaptable to changes in the types of incidents as the conversation evolves.