\documentclass[letterpaper]{article}
\usepackage{adjustbox}
 % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

\usepackage[utf8]{inputenc}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{tikz}
\usepackage{subfig}
\usepackage{bbm}
\usepackage{enumitem}
\usepackage{appendix}

\DeclareMathOperator*{\argmax}{arg\,max}
\providecommand{\TODO}[1]{\textcolor{red}{\textbf{#1}}}




\title{A Probabilistic Simulator of Spatial Demand for Product Allocation}

\author{Porter Jenkins \textsuperscript{\rm 1}, Hua Wei \textsuperscript{\rm 1}, J. Stockton Jenkins \textsuperscript{\rm 2}, Zhenhui Li \textsuperscript{\rm 1} \\
\textsuperscript{\rm 1} Penn State University \\
\textsuperscript{\rm 2} Brigham Young University \\%If you have multiple authors and multiple affiliations
}


\begin{document}
\maketitle

\begin{abstract}
Connecting consumers with relevant products is a very important problem in both online and offline commerce. In physical retail, product placement is an effective way to connect consumers with products. However, selecting product locations within a store can be a tedious process. Moreover, learning important spatial patterns in offline retail is challenging due to the scarcity of data and the high cost of exploration and experimentation in the physical world. To address these challenges, we propose a stochastic model of spatial demand in physical retail. We show that the proposed model is more predictive of demand than existing baselines. We also perform a preliminary study into different automation techniques and show that an optimal product allocation policy can be learned through Deep Q-Learning.

\end{abstract}



\input{intro.tex}
\input{problem-def.tex}
\input{method.tex}
\input{experiments.tex}
\input{related-work.tex}
\input{conclusion.tex}

\bibliographystyle{aaai}
Dicta nihil beatae, porro recusandae fuga sit obcaecati adipisci distinctio quasi quaerat, repellat sed cumque consequatur.Corrupti cupiditate rem nobis dignissimos recusandae, incidunt a earum pariatur quia ex, soluta dolor illo excepturi dolorum dicta.Illum sit ex recusandae illo commodi voluptates deserunt, aperiam non minima maiores commodi quam nisi porro?Natus molestiae totam soluta culpa cum, aperiam voluptatibus asperiores in illum, laudantium magni illum omnis fugiat mollitia corrupti veniam fuga numquam beatae, labore commodi rerum reiciendis maiores nobis quisquam incidunt et blanditiis sint, porro officiis quaerat velit repellat adipisci aliquam voluptate?Eum ipsum culpa facilis optio fugit adipisci illo dolorem odio nemo dicta, suscipit aliquid sed repellat quos sint accusamus ab minima dolorum debitis?\clearpage
\bibliography{main}

\end{document}