\begin{table*}[t]
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|cc|cc|cc}
\toprule
    & CUB-P & CUB-R & House-P& House-R & Zoo-P & Zoo-R \\
\midrule
Hi-Viscont & $91.03 \pm 3.00$ & $63.35\pm 9.69$ & $87.39\pm 1.71$  & $85.89\pm 9.95$ & $85.24\pm 5.41$ & $83.37\pm 15.67$\\
%\midrule
FALCON & $90.60\pm 4.18$  & $62.15\pm 8.38$  & $87.62\pm 1.71$ & $87.04\pm 8.29$ & $84.10\pm 5.86$& $87.41\pm 12.98$\\
\bottomrule
\end{tabular}%
}
\caption{The mean and standard deviation of precision and recall of Hi-Viscont and FALCON on the test concepts across all the three domains.}
\label{tab:detailed_test}
\end{table*}

\begin{table*}[t]
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|cc|cc|cc|cc|cc}
\toprule
    &  Species-P& Species-R & Genera-P & Genera-R & Family-P & Family-R & Order-P & Order-R & Class-P & Class-R\\
\midrule
Hi-Viscont & $98.32\pm 0.63$  & $78.20\pm 3.56$ & $97.06\pm 0.44$ & $84.61\pm 0.90$ & $93.51\pm 2.33$& $88.12\pm 2.08$& $94.68\pm 1.58$& $89.40\pm 1.68$& $1\pm 0.00$ & $93.04\pm 13.71$\\
%\midrule
FALCON & $98.28\pm 0.59$ & $77.35\pm 2.59$& $96.66\pm 0.86$& $81.17\pm 1.24$ & $87.55\pm 3.13$& $81.43\pm 2.40$& $85.70\pm 3.70$& $83.10\pm 5.28$& $1\pm 0.00$ & $98.63\pm 1.85$ \\
\bottomrule
\end{tabular}%
}
\caption{The mean and standard deviation of precision and recall of the two models on CUB-200-2011 dataset by depth of concepts.}
\label{tab:detailed_CUB}
\end{table*}

\begin{table*}[t]
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|cc|cc|cc}
\toprule
    & Object-P & Object-R & Color-P& Color-R & Affordance-P & Affordance-R \\
\midrule
Hi-Viscont & $86.19\pm 1.81$& $90.91\pm 3.08$& $99.94\pm 0.09$& $98.56\pm 1.41$& $95.51\pm 1.34$& $85.89\pm 14.86$\\
%\midrule
FALCON &$87.16\pm 1.43$& $91.57\pm 2.66$& $91.71\pm 2.28$& $83.80\pm 10.07$& $91.37\pm 1.71$& $42.25\pm 9.32$\\
\bottomrule
\end{tabular}%
}
\caption{The mean and standard deviation of precision and recall of the two models on the house domain by type of concepts.}
\label{tab:detailed_house}
\end{table*}

\begin{table*}[t]
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|cc|cc}
\toprule
    & Leaf-P & Leaf-R & Non-leaf-P& Non-Leaf-R\\
\midrule
Hi-Viscont &$82.97\pm 5.32$& $93.89\pm 5.25$&$77.30\pm 7.77$& $96.93 \pm 5.97$\\
%\midrule
FALCON & $84.01\pm 5.29$& $94.90\pm 5.03$& $76.80\pm 4.08$& $58.38\pm 7.09$\\
\bottomrule
\end{tabular}%
}
\caption{The mean and standard deviation of precision and recall for the two models on the zoo domain by type of concepts.}
\label{tab:detailed_zoo}
\end{table*}

\subsection{Detailed Results on VQA}
We present the detailed results and analysis on VQA for each domain. Table~\ref{tab:detailed_test} presents the mean and standard deviation of the precision and recall of Hi-Viscont and FALCON on test concepts across all the three domains. The performance of both model is comparable on the test concepts on both precision and recall because majority of the test concepts are leaf concepts. Table~\ref{tab:detailed_CUB}, Table~\ref{tab:detailed_house}, and Table~\ref{tab:detailed_zoo} present the mean and standard deviation of the precision and recall for the CUB-200-2011 dataset, the house domain, and the zoo domain by the type of concept repectively. For all the three domains, Hi-Viscont consistently outperform FALCON on the recall metric for non-leaf concepts with a large margin because of the active updates from the ARGNN. Such results further demonstrate the importance of the information propagation from children to ancestor nodes in a continual learning setting.

\subsection{Statistic Tests on VQA}
In this section, we presents the statistic tests between Hi-Viscont and FALCON for all the three domains. 
\paragraph{CUB-200-2011.} Results of paired t-test suggest that Hi-Viscont achieves higher F1 scores with significance for concepts in Genera($p<0.001$), Family($p<0.001$), and Order($p=0.005$).
\paragraph{House Construction Domain.} Results of paired t-test suggests that Hi-Viscont achieves higher F1 scores with significance for color concepts($p=0.005$) and affordance concepts($p=0.002$).
\paragraph{Zoo Domain.} Results of paired t-test suggests that Hi-Viscont achieves higher F1 scores with significance for non-leaf concepts($p=0.001$).

%\ngnote{Conditions for normality were not met for the data points to run a t-test. Hence we conducted a Wilcoxon Signed-Rank test to compare .......}



\subsection{Detailed Results on Human Subject Experiments}
We present the results of statistical tests for each scale we measure for the human subject study in detailed in this subsection. 
For each metric, we report the results of a Shapiro-Wilk Normality test. If the data from such metric passes the normality test($p>0.05$), we report the results of a paired t-test.
Otherwise, we report the results of Wilcoxon signed rank test for that metric. 
\paragraph{Trust.} Results from Shapiro Wilk test suggest that our data in the Trust metric satisfies the condition for a parametric test($W=0.960, p=0.599$). Results from paired t-test suggest that Hi-Viscont is considered better than FALCON by users in the Trust metric with significance($t=2.325, p=0.016, df=17$).
\paragraph{SUS.} Results from Shapiro Wilk test suggest that our data in the SUS metric satisfies the condition for a parametric test($W=0.978, p=0.925$). Results from paired t-test suggest that Hi-Viscont is considered better than FALCON by users in the SUS metric with significance($t=2.428, p=0.013, df=17$).
\paragraph{Intelligence.}Results from Shapiro Wilk test suggest that our data in the Intelligence metric satisfies the condition for a parametric test($W=0.956, p=0.520$). Results from paired t-test suggest that Hi-Viscont is considered better than FALCON by users in the Intelligence metric with significance($t=2.591, p=0.010, df=17$).
\paragraph{Natural.}Results from Shapiro Wilk test suggest that our data in the Anthropomorphism metric satisfies the condition for a parametric test($W=0.937, p=0.255$). Results from paired t-test suggest that Hi-Viscont is considered better than FALCON by users in the Anthropomorphism metric with significance($t=2.924, p=0.005, df=17$).
\paragraph{Comparative.}Conditions for normality were not met for the data points to run a t-test. Hence we conducted a Wilcoxon Signed-Rank test to compare Hi-Viscont and FALCON in the comparative metric. Results from Wilcoxon signed-rank test suggest that Hi-Viscont is preferred by user in the direct comparison with FALCON with significance($Z=2.0, p<0.001$).
\paragraph{Success Rate.}Conditions for normality were not met for the data points to run a t-test. Hence we conducted a Wilcoxon Signed-Rank test to compare Hi-Viscont and FALCON in success rate. Results from Wilcoxon signed-rank test suggest that Hi-Viscont is better than FALCON in success rate with significance($Z=0.0, p=0.014$).
\paragraph{Node-level Accuracy.}Conditions for normality were not met for the data points to run a t-test. Hence we conducted a Wilcoxon Signed-Rank test to compare Hi-Viscont and FALCON in node-level accuracy. Results from Wilcoxon signed-rank test suggest that Hi-Viscont is better than FALCON in node-level accuracy with significance($Z=1.5, p=0.005$).


