
\documentclass[sigconf]{aamas}  % do not change this line!

%% your usepackages here, for example:
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{balance} 
%\usepackage{microtype}
\usepackage[linesnumbered,vlined,ruled]{algorithm2e}
\newcommand{\todo}[1]{{\color{red} [[TODO: {#1}]]}}
\newcommand{\question}[1]{{\color{blue} [[Question: {#1}]]}}
\newcommand{\dan}[1]{{\color{blue} [[Dan: {#1}]]}}

%% do not change the following lines
%% do not change the following lines
\setcopyright{ifaamas}  % do not change this line!
\acmDOI{}  % do not change this line!
\acmISBN{}  % do not change this line!
\acmConference[AAMAS'18]{Proc.\@ of the 17th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2018)}{July 10--15, 2018}{Stockholm, Sweden}{M.~Dastani, G.~Sukthankar, E.~Andr\'{e}, S.~Koenig (eds.)}  % do not change this line!
\acmYear{2018}  % do not change this line!
\copyrightyear{2018}  % do not change this line!
\acmPrice{}  % do not change this line!

%% the rest of your preamble here


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{HIGHLIGHTS: Summarizing Agent Behavior to People}  % put your title here!
%\titlenote{Produces the permission block, and copyright information}

% AAMAS: submissions are anonymous for most tracks
%\author{Paper \#148}  % put your paper number here!

%% example of author block for camera ready version of accepted papers: don't use for anonymous submissions
%
\author{Dan Amir}
\affiliation{%
 \institution{The Hebrew University of Jerusalem}
}
\email{dan.amir@mail.huji.ac.il}
\author{Ofra Amir}
\affiliation{%
 \institution{Technion - Israel Institute of Technology}
}
\email{oamir@technion.ac.il}
%\email{trovato@corporation.com}
%


% \author{Lars Th{\o}rv{\"a}ld}
% \authornote{This author is the
%  one who did all the really hard work.}
% \affiliation{%
%  \institution{The Th{\o}rv{\"a}ld Group}
%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%  \city{Hekla} 
%  \country{Iceland}}
% \email{larst@affiliation.org}

% \author{Valerie B\'eranger}
% \affiliation{%
%  \institution{Inria Paris-Rocquencourt}
%  \city{Rocquencourt}
%  \country{France}
% }
% \author{Aparna Patel} 
% \affiliation{%
% \institution{Rajiv Gandhi University}
% \streetaddress{Rono-Hills}
% \city{Doimukh} 
% \state{Arunachal Pradesh}
% \country{India}}
% \author{Huifen Chan}
% \affiliation{%
%  \institution{Tsinghua University}
%  \streetaddress{30 Shuangqing Rd}
%  \city{Haidian Qu} 
%  \state{Beijing Shi}
%  \country{China}
% }

% \author{Charles Palmer}
% \affiliation{%
%  \institution{Palmer Research Laboratories}
%  \streetaddress{8600 Datapoint Drive}
%  \city{San Antonio}
%  \state{Texas} 
%  \postcode{78229}}
% \email{cpalmer@prl.com}

% \author{John Smith}
% \affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
% \email{jsmith@affiliation.org}

% \author{Julius P.~Kumquat}
% \affiliation{\institution{The Kumquat Consortium}}
% \email{jpkumquat@consortium.net}
%
%% The example's default list of authors is too long for headers
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}  % put your abstract here!
People increasingly interact with autonomous agents. This paper introduces and formalizes the problem of automatically generating a summary of an agent's behavior with the goal of increasing people's familiarity with the agent's capabilities and limitations. In contrast with prior approaches  which developed methods for explaining a single decision made by an agent, our approach aims to provide users with a summary that describes the agent's behavior in different situations. We hypothesize that reviewing such summaries could help people in tasks such as choosing between agents or determining the level of autonomy to grant to an agent. We develop ``HIGHLIGHTS'', an algorithm that produces a summary of an agent's behavior by extracting important trajectories from simulations of the agent. 
We conducted a human-subject experiment to evaluate whether HIGHLIGHTS summaries help people assess the capabilities of agents. Our results show that participants were more successful at evaluating the capabilities of agents when presented with HIGHLIGHTS summaries compared to baseline summaries, and rated them as more helpful. We also explore a variant of the HIGHLIGHTS algorithm which aims to increase the diversity of states included in the summary, and show that this modification further improves people's ability to assess agents' capabilities.

\end{abstract}



\keywords{Strategy summarization, Explainable AI}  % put your semicolon-separated 
%Explainable AI;Agent-Human Interaction
\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% start of main body of paper

\input{intro}
\input{related}
\input{problem}
\input{highlights}
\input{empirical}
\input{experiment1}
\input{experiment2}
\input{disc}

\begin{acks}
%\textbf{Acknowledgements.} 
We thank Avi Segal, Ken Arnold and Sebastian Gehrmann for their feedback on drafts of this paper.
\end{acks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% bibliography: see CFP for number of permitted pages

\bibliographystyle{ACM-Reference-Format}  % do not change this line!
\balance
\bibliography{lib}  % put name of your .bib file here

\end{document}
