Prior work that considered MAPF as a pebble motion 
Vertex conflicts are not allowed in all classical MAPF problems. Disallowing edge conflicts is also known as the \emph{no-swap} constraint. Allowing train conflicts is also referred to as allowing a \emph{train  movement}. By definition, disallowing a train movement also imposes the no-swap constraint. In addition, disallowing $k$-robust vertex conflicts for any $k>1$ also disallows train conflicts.




There are several extensions 
To summarize, the classical MAPF setting assumes the following:
\begin{itemize}
    \item The graph is not weighted, that is all actions cost the same.
    \item Each agent occupies exactly one vertex in the graph.
    \item Time is discretized.
\end{itemize}


Orthogonal to these definitions of a conflict, are the following parametric types of conflicts:
\begin{itemize}
\item $k$-robust conflict. This is a conflict that occurs if one of the agents will not perform its planned action for $k$ time steps. For example, a $k$-robust vertex conflict between  two single-agent plans $\pi_i$ and $\pi_j$ occurs if there exists $t$ such that $\pi_i[t+k]=\pi_j[t]$. 
\item $l$-capacity conflict. This conflict Occurs when $\delta$ or more agents occupy a vertex or an edge. For example, a $l$-capacity vertex conflict occurs if there are $\delta$ single agent plans $\pi_i, \pi_{i+1},\ldots, \pi_{i+l}$ and a time step $t$ such that $\pi_i[t]=\pi_{i+1}[t]=\cdots \pi_l[t]$. 
\end{itemize}


\subsection{Following variants}




\end{itemize}

\section{Objective Functions}
Let $\pi=(\pi_1,\ldots,\pi_k)$ be a solution to a classical MAPF. 
The two most common functions used for evaluating a solution are \emph{makespan} and \emph{sum of costs}. 
\begin{itemize}
\item \textbf{Makespan.} The number of time steps required for all agents to reach their goal. The makespan of $\pi$ is $\max_{1\leq i\leq k} |\pi_i|$. 
\item \textbf{Sum of costs.} Also known as \emph{flowspan}, the sum of time steps required by each agent to reach its goal. The sum of costs of $\pi$ is $\sum_{1\leq i\leq k} |\pi_i|$. 
\item \textbf{Sum of fuel.} The total non-waiting actions required to reach the goal. We sum this over all agents.
\item \textbf{Sum of time off goal.} The time spent by the agent not in the goal location. We sum this over all agents.

\item \textbf{Time before final reach of goal.} The time spent by the agent until it reached its goal for the last time. For example, assume that an agent reached its goal at $t_1$ but then moved away at $t_2$ and arrived again at the goal at time $t_3$ and stayed there forever. Its cost is therefore $t_3$. By contrast, the {\em Time off goal} variant will incur a cost of $t_1$ + $t_3 - t_2$.[[AF: Guni used this variant in many of his experiments.]] We note that the aggregated cost of this variant is not consistent. Because when the agent moves away at $t_2$ its cost jumps right away from $t_1$ to $t_2$. [[AF: This is why I hated this variant all those years, but Guni liked it]]

\item \textbf{Makespan then sum of costs} Among all solutions with the same makespan, choose the one with the lowest sum-of-costs. [[Eli: Pavel uses this one, at least in one paper]]

\end{itemize}

If the agent at goal behavior is \emph{stay at goal} and the objective function is \emph{sum of costs}, then one needs to specify how does staying at a goal affects the sum of costs. A common assumption is that an agent staying in its goal counts as a wait action, unless it is not planned to move away from its goal location. For example, assume that agent $i$ reaches its goal at time step $t$, leaves its goal at time step $t'$, 
arrives back to its goal at time step $t''$, 
and then stays at its goal until all agents reach their goal. 
Then this single-agent plan will contribute $t''$ to the sum of costs of the corresponding solution. 
One can define other ways to compute the sum of cost when the agent behavior is stay at goal, e.g., not counting wait actions of an agent done in its goal. 

[[AF: see my last item]]




\item \textbf{Weighted graphs.} In such a map, every location represents a Euclidean point ($x,y$), and the edges represent allowed move actions. In such map as well we will have actions with different costs, correponding to the weight of the edges in the graph.
\item \textbf{$2^n$-connected grids.} Such maps are a restricted form of weighted graphs in which every location represents a cell in a two-dimensional grid. The move actions of an agent in a cell are all its $2^n$ neighboring cell. When $n>2$, this introduces actions with different costs. For example, in an 8-connected grid a diagonal move costs $\sqrt{2}$ while a move in one of the cardinal directions costs 1. 
\item \textbf{Continuous maps.} In such a map there is no notion of vertices and edges. Each agent may potentially occupy any location and the space of possible actions to perform as well as locations to occupy, is infinite.
\item \textbf{Lattices.} This is a graph where every node is on a grid location, but there are (potentially complex) curves that determine the actions available to each agent.

\end{itemize}





While allowing actions with different durations seems like a small change, it actually impacts quite a few MAPF solvers, and requires some additional definitions and assumptions. 



Two alternative meanings to edge weights have been studied. 
\comment{Hang: The discussion on "costs" intersects with the earlier section on "objective functions".}\comment{Roni: Tried to address this.}
\begin{itemize}
	\item \textbf{Edge weight is traversal time.} In this option, the cost of an action is the time required for the agent to perform it. 
    \item \textbf{Cost is not time.} In this option, the time required to perform all actions is still one time step, and the actions cost represent another objective that the MAPF solver aims to optimize. Such a cost can be, for example, the cost of driving in a toll road. 
\end{itemize}

The above types of maps were described in the context of 2 dimensional terrains. However, MAPF on higher dimensional maps is also possible. 


The exact meaning of these costs must be defined, as it depends on the problem setting. 
\comment{Hang: The discussion on "costs" intersects with the earlier section on "objective functions".}
\comment{Roni: yes,good point. I will mention this}
\begin{itemize}
	\item \textbf{Edge cost represent action duration.} In this option, 
	the cost of an action is the time required for the agent to perform it. 
	Prior work that assumed this includes~\cite{bartak2018aScheduling,walker2018extended}. 
    \item \textbf{Edge cost may be different from action duration.}  In this option, 
    the cost of an action is a different objective that the MAPF solver aims to optimize. 
    For example, such a cost can be the cost of driving in a toll road.
\end{itemize}
Not
In the latter option, one needs to also define the duration of each action. time required to traverse each edge. 
That is 
the time required to perform all actions is still one time step, and 

, or a mechanism for 
    giving priority to some agents by making their movement actions more costly~\cite{bartak2017modeling}
where $G=(V,E)$ is a directed graph,


\begin{itemize}
    \item \textbf{Weighted graphs.} MAPF
    In such a map, every location represents a Euclidean point ($x,y$), and the edges represent allowed move actions. In such map as well we will have actions with different costs, correponding to the weight of the edges in the graph.
\end{itemize}





The semantics of the weight of 


\section{Types of Maps}
The map where the agents move in is an unweighted graph in Classical MAPF. 1
Research on MAPF has explored other possibilities. In these variants, agents occupy a nonzero area or volume and conflicts occur when two (or more) agents overlap at the same time. \comment{Hang: This section might be closely related to "agent at goal behavior". In general, "types of graphs", together with the positions of start and goal vertices, can change the solvability of different algorithms. Think of graphs with at least two unoccupied vertices for Push-and-Rotate and "well-formed" instances for prioritized algorithms. For the general problem definition, I always use the special case of a "connected undirected graph". Relaxing it to a "directed graph" might have an impact on some algorithms.}

\begin{itemize}
\item \textbf{Weighted graphs.} In such a map, every location represents a Euclidean point ($x,y$), and the edges represent allowed move actions. In such map as well we will have actions with different costs, correponding to the weight of the edges in the graph.
\item \textbf{$2^n$-connected grids.} Such maps are a restricted form of weighted graphs in which every location represents a cell in a two-dimensional grid. The move actions of an agent in a cell are all its $2^n$ neighboring cell. When $n>2$, this introduces actions with different costs. For example, in an 8-connected grid a diagonal move costs $\sqrt{2}$ while a move in one of the cardinal directions costs 1. 
\item \textbf{Continuous maps.} In such a map there is no notion of vertices and edges. Each agent may potentially occupy any location and the space of possible actions to perform as well as locations to occupy, is infinite.
\item \textbf{Lattices.} This is a graph where every node is on a grid location, but there are (potentially complex) curves that determine the actions available to each agent.

\end{itemize}
In all types of maps actions may have different costs. 
How this cost is considered is another design choice that depend on the problem setting. \comment{Hang: The discussion on "costs" intersects with the earlier section on "objective functions".}
\begin{itemize}
	\item \textbf{Cost is time.} In this option, the cost of an action is the time required for the agent to perform it. 
    \item \textbf{Cost is not time.} In this option, the time required to perform all actions is still one time step, and the actions cost represent another objective that the MAPF solver aims to optimize. Such a cost can be, for example, the cost of driving in a toll road. 
\end{itemize}

The above types of maps were described in the context of 2 dimensional terrains. However, MAPF on higher dimensional maps is also possible. 





The map where the agents move in is an unweighted graph in Classical MAPF. 1
Research on MAPF has explored other possibilities. In these variants, agents occupy a nonzero area or volume and conflicts occur when two (or more) agents overlap at the same time. \comment{Hang: This section might be closely related to "agent at goal behavior". In general, "types of graphs", together with the positions of start and goal vertices, can change the solvability of different algorithms. Think of graphs with at least two unoccupied vertices for Push-and-Rotate and "well-formed" instances for prioritized algorithms. For the general problem definition, I always use the special case of a "connected undirected graph". Relaxing it to a "directed graph" might have an impact on some algorithms.}




\section{Drafts}



% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\small
\begin{tabular}{@{}llrr@{}}
\toprule
Type & Map Name                  & Height & Width \\ \midrule
DAO     & brc202d.map               & 481    & 530   \\
DAO     & den312d.map               & 81     & 65    \\
DAO     & den520d.map               & 257    & 256   \\
DAO     & orz900d.map               & 656    & 1491  \\
DAO     & ost003d.map               & 194    & 194   \\
DAO     & lak303d.map               & 194    & 194   \\
Dragon Age 2     & ht\_chantry.map           & 141    & 162   \\
Dragon Age 2     & ht\_mansion\_n.map        & 270    & 133   \\
Dragon Age 2     & w\_woundedcoast.map       & 578    & 642   \\ 
Dragon Age 2     & lt\_gallowstemplar\_n.map & 180    & 251   \\
Open     & empty-16-16.map           & 16     & 16    \\
Open     & empty-32-32.map           & 32     & 32    \\
Open     & empty-48-48.map           & 48     & 48    \\
Open     & empty-8-8.map             & 8      & 8     \\
Open+obstacles     & random-32-32-10.map       & 32     & 32    \\
Open+obstacles     & random-32-32-20.map       & 32     & 32    \\
Open+obstacles     & random-64-64-10.map       & 64     & 64    \\
Open+obstacles     & random-64-64-20.map       & 64     & 64    \\
Open+obstacles     & random-32-32-10.map       & 32     & 32    \\
Open+obstacles     & random-32-32-20.map       & 32     & 32    \\
Open+obstacles     & random-64-64-10.map       & 64     & 64    \\
Open+obstacles     & random-64-64-20.map       & 64     & 64    \\
City     & Berlin\_1\_256.map        & 256    & 256   \\
City     & Boston\_0\_256.map        & 256    & 256   \\
City     & Paris\_1\_256.map         & 256    & 256   \\
Maze     & maze-128-128-10.map       & 128    & 128   \\
Maze & maze-128-128-2.map        & 128    & 128   \\
Maze     & maze-32-32-2.map          & 32     & 32    \\
Maze     & maze-32-32-4.map          & 32     & 32    \\
Room     & room-32-32-4.map          & 32     & 32    \\
Room     & room-32-32-8.map          & 32     & 32    \\
Room     & room-64-64-16.map         & 64     & 64    \\
Room     & room-64-64-8.map          & 64     & 64    \\
\bottomrule
\end{tabular}
\caption{The grids available in the grid \mapf benchmark.}
\label{tab:gridmaps}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[]
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}llcrrrrrrrrrrrrrrrrrrrrrrrrr@{}}
               &                           &            & \multicolumn{25}{c}{Scenario}                                    \\ \midrule
Type           & \multicolumn{1}{r}{Map}   & Size       & \multicolumn{1}{r}{1}  & \multicolumn{1}{r}{2}  & \multicolumn{1}{r}{3}  & \multicolumn{1}{r}{4}  & \multicolumn{1}{r}{5}  & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{8}  & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{10} & \multicolumn{1}{r}{11} & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{19} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{25} \\ \midrule
City           & Berlin\_1\_256.map        & 256 X 256  & \multicolumn{1}{r}{39} & \multicolumn{1}{r}{40} & \multicolumn{1}{r}{30} & \multicolumn{1}{r}{44} & \multicolumn{1}{r}{43} & \multicolumn{1}{r}{40} & \multicolumn{1}{r}{37} & \multicolumn{1}{r}{41} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{43} & \multicolumn{1}{r}{38} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{37} & \multicolumn{1}{r}{30} & \multicolumn{1}{r}{32} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{37} & \multicolumn{1}{r}{41} & \multicolumn{1}{r}{38} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{27} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{29} \\
City           & Boston\_0\_256.map        & 256 X 256  & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{11} & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{8}  & \multicolumn{1}{r}{37} & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{31} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{31} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{35} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{15} \\
DAO            & brc202d.map               & 481 X 530  & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{11} & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{11} & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{12} & \multicolumn{1}{r}{10} & \multicolumn{1}{r}{14} \\
DAO            & den312d.map               & 81 X 65    & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{27} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{20} \\
DAO            & den520d.map               & 257 X 256  & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{33} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{9}  & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{8}  & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{8}  & \multicolumn{1}{r}{27} & \multicolumn{1}{r}{39} & \multicolumn{1}{r}{32} & \multicolumn{1}{r}{39} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{35} & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{6}  & \multicolumn{1}{r}{7}  & \multicolumn{1}{r}{34} \\
Open           & empty-16-16.map           & 16 X 16    & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{43} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{42} & \multicolumn{1}{r}{46} & \multicolumn{1}{r}{48} & \multicolumn{1}{r}{46} & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{41} & \multicolumn{1}{r}{43} & \multicolumn{1}{r}{42} & \multicolumn{1}{r}{41} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{48} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{45} & \multicolumn{1}{r}{46} & \multicolumn{1}{r}{38} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{44} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{31} & \multicolumn{1}{r}{13} \\
Open           & empty-32-32.map           & 32 X 32    & \multicolumn{1}{r}{41} & \multicolumn{1}{r}{34} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{38} & \multicolumn{1}{r}{70} & \multicolumn{1}{r}{70} & \multicolumn{1}{r}{28} & \multicolumn{1}{r}{30} & \multicolumn{1}{r}{61} & \multicolumn{1}{r}{57} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{49} & \multicolumn{1}{r}{5}  & \multicolumn{1}{r}{39} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{65} & \multicolumn{1}{r}{35} & \multicolumn{1}{r}{87} & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{47} & \multicolumn{1}{r}{84} & \multicolumn{1}{r}{13} & \multicolumn{1}{r}{30} & \multicolumn{1}{r}{23} \\
Open           & empty-48-48.map           & 48 X 48    & \multicolumn{1}{r}{83} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{70} & \multicolumn{1}{r}{40} & \multicolumn{1}{r}{33} & \multicolumn{1}{r}{71} & \multicolumn{1}{r}{78} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{71} & \multicolumn{1}{r}{62} & \multicolumn{1}{r}{50} & \multicolumn{1}{r}{30} & \multicolumn{1}{r}{40} & \multicolumn{1}{r}{24} & \multicolumn{1}{r}{67} & \multicolumn{1}{r}{26} & \multicolumn{1}{r}{49} & \multicolumn{1}{r}{43} & \multicolumn{1}{r}{33} & \multicolumn{1}{r}{61} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{37} & \multicolumn{1}{r}{36} & \multicolumn{1}{r}{40} & \multicolumn{1}{r}{25} \\
Open           & empty-8-8.map             & 8 X 8      & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{19} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{25} & \multicolumn{1}{r}{20} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{19} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{19} \\
Dragon Age 2   & ht\_chantry.map           & 141 X 162  & \multicolumn{1}{r}{18} & \multicolumn{1}{r}{23} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{21} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{22} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{14} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{15} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{16} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{17} & \multicolumn{1}{r}{21} \\
Dragon Age 2   & ht\_mansion\_n.map        & 270 X 133  & 27                     & 15                     & 28                     & 28                     & 30                     & 25                     & 35                     & 28                     & 24                     & 31                     & 26                     & 22                     & 25                     & 5                      & 24                     & 30                     & 20                     & 31                     & 19                     & 28                     & 29                     & 22                     & 31                     & 22                     & 20                     \\
DAO            & lak303d.map               & 194 X 194  & 13                     & 6                      & 11                     & 5                      & 17                     & 9                      & 11                     & 12                     & 9                      & 6                      & 16                     & 12                     & 16                     & 16                     & 22                     & 24                     & 14                     & 9                      & 12                     & 11                     & 10                     & 13                     & 17                     & 13                     & 7                      \\
Dragon Age 2   & lt\_gallowstemplar\_n.map & 180 X 251  & 13                     & 10                     & 14                     & 9                      & 12                     & 18                     & 15                     & 8                      & 18                     & 10                     & 26                     & 9                      & 9                      & 15                     & 18                     & 10                     & 11                     & 11                     & 18                     & 21                     & 8                      & 25                     & 11                     & 11                     & 19                     \\
Maze           & maze-128-128-10.map       & 128 X 128  & 11                     & 9                      & 11                     & 5                      & 5                      & 6                      & 5                      & 3                      & 6                      & 9                      & 5                      & 6                      & 6                      & 4                      & 5                      & 5                      & 6                      & 7                      & 6                      & 5                      & 6                      & 6                      & 10                     & 5                      & 6                      \\
Maze           & maze-128-128-2.map        & 128 X 128  & 5                      & 6                      & 5                      & 7                      & 8                      & 6                      & 5                      & 5                      & 8                      & 4                      & 9                      & 5                      & 11                     & 7                      & 8                      & 7                      & 8                      & 5                      & 10                     & 8                      & 2                      & 10                     & 9                      & 10                     & 7                      \\
Maze           & maze-32-32-2.map          & 32 X 32    & 13                     & 15                     & 15                     & 5                      & 21                     & 10                     & 21                     & 19                     & 11                     & 13                     & 8                      & 9                      & 9                      & 8                      & 12                     & 11                     & 13                     & 11                     & 10                     & 9                      & 13                     & 12                     & 13                     & 11                     & 14                     \\
Maze           & maze-32-32-4.map          & 32 X 32    & 3                      & 8                      & 18                     & 8                      & 8                      & 5                      & 4                      & 3                      & 8                      & 3                      & 20                     & 2                      & 24                     & 7                      & 8                      & 15                     & 14                     & 7                      & 14                     & 15                     & 9                      & 18                     & 14                     & 16                     & 19                     \\
DAO            & orz900d.map               & 656 X 1491 & 6                      & 10                     & 9                      & 4                      & 6                      & 4                      & 5                      & 4                      & 4                      & 5                      & 5                      & 10                     & 8                      & 4                      & 9                      & 9                      & 6                      & 7                      & 10                     & 5                      & 7                      & 5                      & 5                      & 7                      & 3                      \\
DAO            & ost003d.map               & 194 X 194  & 9                      & 14                     & 11                     & 6                      & 7                      & 10                     & 23                     & 19                     & 23                     & 23                     & 31                     & 14                     & 25                     & 14                     & 28                     & 19                     & 9                      & 11                     & 31                     & 19                     & 11                     & 19                     & 9                      & 7                      & 31                     \\
Paris\_1\_256  & Paris\_1\_256.map         & 256 X 256  & 27                     & 34                     & 28                     & 19                     & 30                     & 30                     & 26                     & 27                     & 27                     & 13                     & 32                     & 36                     & 29                     & 28                     & 29                     & 35                     & 19                     & 21                     & 31                     & 32                     & 30                     & 31                     & 30                     & 22                     & 31                     \\
Open+obstacles & random-32-32-10.map       & 32 X 32    & 23                     & 23                     & 23                     & 23                     & 23                     & 23                     & 50                     & 45                     & 44                     & 50                     & 10                     & 60                     & 55                     & 68                     & 61                     & 60                     & 54                     & 60                     & 56                     & 29                     & 42                     & 40                     & 63                     & 44                     & 49                     \\
Open+obstacles & random-32-32-20.map       & 32 X 32    & 45                     & 41                     & 34                     & 26                     & 26                     & 29                     & 35                     & 25                     & 41                     & 40                     & 33                     & 39                     & 39                     & 34                     & 32                     & 30                     & 35                     & 22                     & 46                     & 41                     & 13                     & 32                     & 15                     & 22                     & 34                     \\
Open+obstacles & random-64-64-10.map       & 64 X 64    & 58                     & 16                     & 91                     & 55                     & 16                     & 78                     & 78                     & 77                     & 76                     & 73                     & 45                     & 45                     & 63                     & 80                     & 45                     & 67                     & 67                     & 67                     & 67                     & 67                     & 25                     & 64                     & 25                     & 63                     & 11                     \\
Open+obstacles & random-64-64-20.map       & 64 X 64    & 68                     & 30                     & 39                     & 48                     & 63                     & 48                     & 47                     & 43                     & 63                     & 57                     & 46                     & 61                     & 43                     & 20                     & 49                     & 20                     & 50                     & 20                     & 20                     & 49                     & 40                     & 28                     & 28                     & 40                     & 56                     \\
Room           & room-32-32-4.map          & 32 X 32    & 57                     & 67                     & 70                     & 38                     & 57                     & 38                     & 39                     & 38                     & 54                     & 67                     & 64                     & 38                     & 38                     & 38                     & 43                     & 83                     & 41                     & 77                     & 64                     & 77                     & 62                     & 46                     & 77                     & 53                     & 61                     \\
Room           & room-32-32-8.map          & 32 X 32    & 12                     & 9                      & 13                     & 12                     & 11                     & 13                     & 14                     & 13                     & 8                      & 10                     & 13                     & 11                     & 14                     & 15                     & 15                     & 15                     & 15                     & 11                     & 8                      & 15                     & 13                     & 11                     & 9                      & 12                     & 20                     \\
Room           & room-64-64-16.map         & 64 X 64    & 30                     & 30                     & 43                     & 39                     & 32                     & 32                     & 37                     & 21                     & 21                     & 19                     & 32                     & 38                     & 26                     & 27                     & 30                     & 33                     & 27                     & 33                     & 33                     & 30                     & 30                     & 30                     & 47                     & 31                     & 46                     \\
Room           & room-64-64-8.map          & 64 X 64    & 13                     & 11                     & 16                     & 11                     & 18                     & 19                     & 18                     & 16                     & 14                     & 18                     & 8                      & 9                      & 17                     & 18                     & 19                     & 18                     & 17                     & 18                     & 14                     & 20                     & 16                     & 16                     & 17                     & 18                     & 19                     \\
Dragon Age 2   & w\_woundedcoast.map       & 578 X 642  & 5                      & 17                     & 10                     & 13                     & 14                     & 5                      & 5                      & 4                      & 12                     & 11                     & 11                     & 9                      & 18                     & 12                     & 7                      & 13                     & 9                      & 14                     & 10                     & 10                     & 14                     & 12                     & 7                      & 19                     & 14                     \\ \bottomrule
\end{tabular}
}
\end{table*}




% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
\begin{table*}[]
\begin{tabular}{@{}lll|rrrr|rrrr@{}}
\toprule
                                &                       &            & \multicolumn{4}{c}{Random assignment}                                                                    & \multicolumn{4}{c}{Even-distance assignment}                                                             \\ \midrule
Type                            & Map                   & Size       & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Solved} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Solved} & \multicolumn{1}{c}{All} \\ 
\toprule
\multirow{3}{*}{City}                            & Berlin\_1\_256        & 256 X 256  & 9                       & 49                      & 904                        & 25000                   & 16                      & 44                      & 864                        & 24150                   \\
                            & Boston\_0\_256        & 256 X 256  & 10                      & 51                      & 693                        & 25000                   & 8                       & 37                      & 571                        & 23720                   \\
                            & Paris\_1\_256         & 256 X 256  & 16                      & 50                      & 939                        & 25000                   & 13                      & 36                      & 697                        & 26390                   \\
\midrule \multirow{6}{*}{DAO}            & brc202d               & 481 X 530  & 6                       & 13                      & 219                        & 25000                   & 6                       & 18                      & 247                        & 62030                   \\
                                & den312d               & 81 X 65    & 12                      & 41                      & 543                        & 25000                   & 15                      & 27                      & 556                        & 7050                    \\
                                & den520d               & 257 X 256  & 11                      & 47                      & 734                        & 25000                   & 6                       & 39                      & 549                        & 21640                   \\
                                & lak303d               & 194 X 194  & 11                      & 30                      & 471                        & 25000                   & 5                       & 24                      & 311                        & 25660                   \\
                                & orz900d               & 656 X 1491 & 5                       & 8                       & 139                        & 25000                   & 3                       & 10                      & 157                        & 161070                  \\
                                & ost003d               & 194 X 194  & 14                      & 37                      & 544                        & 25000                   & 6                       & 31                      & 423                        & 20480                   \\
\midrule \multirow{4}{*}{Dragon Age 2}   & ht\_chantry           & 141 X 162  & 16                      & 42                      & 583                        & 25000                   & 14                      & 23                      & 420                        & 11550                   \\
                                & ht\_mansion\_n        & 270 X 133  & 19                      & 48                      & 794                        & 25000                   & 5                       & 35                      & 625                        & 14020                   \\
                                & w\_woundedcoast       & 578 X 642  & 5                       & 21                      & 332                        & 25000                   & 4                       & 19                      & 275                        & 52520                   \\
                                & lt\_gallowstemplar\_n & 180 X 251  & 9                       & 20                      & 374                        & 25000                   & 8                       & 26                      & 349                        & 15400                   \\
\midrule \multirow{4}{*}{Open}           & empty-16-16           & 16 X 16    & 2                       & 49                      & 781                        & 3200                    & 13                      & 48                      & 886                        & 3200                    \\
                                & empty-32-32           & 32 X 32    & 8                       & 70                      & 1124                       & 12800                   & 5                       & 87                      & 1010                       & 12800                   \\
                                & empty-48-48           & 48 X 48    & 34                      & 105                     & 1486                       & 25000                   & 18                      & 83                      & 1144                       & 28800                   \\
                                & empty-8-8             & 8 X 8      & 17                      & 26                      & 517                        & 800                     & 15                      & 25                      & 514                        & 800                     \\
\midrule \multirow{4}{*}{Open+obstacles} & random-32-32-10       & 32 X 32    & 15                      & 59                      & 1072                       & 11525                   & 10                      & 68                      & 1078                       & 2470                    \\
                                & random-32-32-20       & 32 X 32    & 24                      & 44                      & 862                        & 10225                   & 13                      & 46                      & 809                        & 2650                    \\
                                & random-64-64-10       & 64 X 64    & 10                      & 81                      & 1216                       & 25000                   & 11                      & 91                      & 1419                       & 5160                    \\
                                & random-64-64-20       & 64 X 64    & 28                      & 73                      & 1273                       & 25000                   & 20                      & 68                      & 1076                       & 5520                    \\
\midrule \multirow{4}{*}{Maze}           & maze-128-128-10       & 128 X 128  & 6                       & 24                      & 327                        & 25000                   & 3                       & 11                      & 158                        & 27050                   \\
                                & maze-128-128-2        & 128 X 128  & 5                       & 12                      & 170                        & 25000                   & 2                       & 11                      & 175                        & 64690                   \\
                                & maze-32-32-2          & 32 X 32    & 6                       & 20                      & 307                        & 8325                    & 5                       & 21                      & 306                        & 5960                    \\
                                & maze-32-32-4          & 32 X 32    & 7                       & 23                      & 367                        & 9875                    & 2                       & 24                      & 270                        & 5100                    \\
\midrule \multirow{4}{*}{Room}           & room-32-32-4          & 32 X 32    & 29                      & 29                      & 725                        & 12800                   & 38                      & 83                      & 1387                       & 2350                    \\
                                & room-32-32-8          & 32 X 32    & 13                      & 13                      & 325                        & 10100                   & 8                       & 20                      & 312                        & 4180                    \\
                                & room-64-64-16         & 64 X 64    & 17                      & 46                      & 732                        & 25000                   & 19                      & 47                      & 797                        & 5680                    \\
                                & room-64-64-8          & 64 X 64    & 5                       & 17                      & 302                        & 25000                   & 8                       & 20                      & 398                        & 7780                    \\ \bottomrule
\end{tabular}
\caption{Results of running ICBS on problems from the grid \mapf benchmark.} 
\label{tab:results}
\end{table*}