\subsection*{COMET generations}

COMET goal generations:
\begin{itemize}
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to clear the air
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to be safe
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to be unpredictable
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to show off
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to forecast
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to prepare
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to have a good time
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to prepare for a storm
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to have a good experience
\item IF there are thunderstorms in the forecast within a few hours THEN remind me to close the windows BECAUSE I WANT to make sure everything is safe
\end{itemize}

COMET action generations:
\begin{itemize}
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to enjoy the weather BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to be safe BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to have fun BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to take pictures BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to take a break BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to have a good time BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to relax BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to enjoy a good time BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to go to the store BECAUSE i want to keep my home dry.
\item IF there are thunderstorms in the forecast within a few hours THEN I WANT to make sure everything is fine BECAUSE i want to keep my home dry.
\end{itemize}