\def\year{2021}\relax
%File: formatting-instructions-latex-2021.tex
%release 2021.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS


\usepackage{cite}
\usepackage{amssymb} 
\usepackage{amstext}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage[switch]{lineno}



%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
\pdfinfo{
/Title (A Graph-based Relevance Matching Model for Ad-hoc Retrieval)
/Author (Yufeng Zhang, Jinghao Zhang, Zeyu Cui, Shu Wu, Liang Wang)
/TemplateVersion (2021.1)
} %Leave this
% /Title ()
% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
% Leave the space between \Title and the beginning parenthesis alone
% /Author ()
% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case.
% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands,


\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai21.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash

\title{A Graph-based Relevance Matching Model for Ad-hoc Retrieval}
\author{\textbf{Yufeng Zhang\textsuperscript{\rm 1}\thanks{Equal contribution}, Jinghao Zhang\textsuperscript{\rm 1,\rm 2}\footnotemark[1], Zeyu Cui\textsuperscript{\rm 1,\rm 2}, Shu Wu\textsuperscript{\rm 1,\rm2,\rm 3}\thanks{Corresponding author} and Liang Wang\textsuperscript{\rm 1,\rm 2}} \\
}
\affiliations{\textsuperscript{\rm 1}Institute of Automation, Chinese Academy of Sciences \\
  \textsuperscript{\rm 2}University of Chinese Academy of Sciences \\
  \textsuperscript{\rm 3}Artificial Intelligence Research, Chinese Academy of Sciences \\
  \texttt{\{yufeng.zhang,jinghao.zhang\}@cripac.ia.ac.cn} \\ \texttt{\{zeyu.cui,shu.wu,wangliang\}@nlpr.ia.ac.cn}\\}

\begin{document}

\maketitle

\begin{abstract}
To retrieve more relevant, appropriate and useful documents given a query, finding clues about that query through the text is crucial. Recent deep learning models regard the task as a term-level matching problem, which seeks exact or similar query patterns in the document. However, we argue that they are inherently based on local interactions and do not generalise to ubiquitous, non-consecutive contextual relationships. In this work, we propose a novel relevance matching model based on graph neural networks to leverage the document-level word relationships for ad-hoc retrieval. In addition to the local interactions, we explicitly incorporate all contexts of a term through the graph-of-word text format. Matching patterns can be revealed accordingly to provide a more accurate relevance score. Our approach significantly outperforms strong baselines on two ad-hoc benchmarks. We also experimentally compare our model with BERT and show our advantages on long documents.



\end{abstract}

\input{body/intro}

\input{body/relatedwork}

\input{body/model}

\input{body/exp}

\input{body/conclusion}

\input{body/acknowledgement}

\bibliography{ref.bib}
\end{document}
